Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\extraspacing {\bf Computing the ``d-cross'' Sets.} We are ready explain how to compute $\dcross_H(\bm{t})$ for any $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. By Statement (2) of Lemma~\ref{lmm:hv:type1:cross-r*},

>>>>

\extraspacing {\bf Computing the ``d-cross'' Sets.} We are ready explain how to compute $\dcross_H(\bm{t})$, defined in \eqref{eqn:dcross-H}, for any $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. This, in fact, has been made easy by Statement (2) of Lemma~\ref{lmm:hv:type1:cross-r*}. First, identify the rectangle $r' = \gbot(\bm{t})$ and fetch its (already computed) top-sliced rectangle $r^*$. Second, compute $B_\bm{t}$ and $\gleft(\bm{t})$. These two steps require $O(k)$ time. Then, scan the segments in $\cross_H(r^*)$ in ascending order of their y-coordinates. For each segment $h$ scanned, check whether $h$ belongs to $\dcross_H(\bm{t})$, namely,  whether $h$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$; this can be done in constant time. Abort the scan as soon as $h \notin \dcross_H(\bm{t})$. This way, we produce $\dcross_H(\bm{t})$ in $O(k + |\dcross_H(\bm{t}|)$ time. Doing so for all $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ takes $O(k |\J| + |\J^*|) = O(k \cdot \out)$ time.
